The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-12-07 document/ms.tex
added outline material

\section{Parameters}

>>>>

\section{Data}

Kepler data here.

Cut out bits around the transits, masking, etc.

Pre-conditioning by doing the local linear fits.

What gets passed forward:  Flattened light curve bits plus ivars?

\section{Model}

A model, from our perspective,
is a parameterized probability for the data,
and a prior probability distribution over parameters.
For the probability of the data, we do [XXX chi-squared].
